---
title: "great_wine_project"
author: "Henry Oamen"
date: "01/06/2024"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# The Great Wine Company

### Company overview: 
Wine is all about people. We are a company run by wine people. We offer free UK delivery on orders over £500 and 10% off orders of 120+ bottles. We list over 130k wines from over 130 fabulous winemakers across the world in more than 44 countries. We know each of our producers personally. We want to continue to enjoy monopoly and expand into other countries where we are not yet dominant. 

### Project scope: 
We now require an analyst to help provide insight into our business. We would like to know which countries produce the finest quality wine (we rate high quality wine as wine with points equal or above 90). Which of our products is the most expensive and which producer makes this. Which products should we not supply anymore, with points less than 45. Please provide a report for the next meeting with the programme director, include some beautiful graphs 


## Loading necessary packages

```{r}
library(tidyverse)
```

```{r}
library(readxl)
```
## Reading in our data

```{r}
data <- read_csv("winemag-data-130k-v2.csv", na = "")

data(head)
```


## Exploring our data

```{r}
glimpse(data)
```


```{r}
colnames(data)
```

```{r}
head(data)
```



```{r}
# to check if there are NaN values in the dataset

any(is.na(data))
```


## Filtering required dataset to exclude NaN values

```{r}
# we can exclude the rows with NaN values

filtered_data <- 
  
  filter(data, country!='NA' & points!='NA' & price!='NA' & province!='NA' & designation != 'NA') 

```

### 1. To determine which country produced the finest quality wine based on points

```{r}
# select desired columns
country_points <- 
  
  filtered_data[c('country', 'points', 'price')] 

country_points
```


```{r}
# plot a graph to see the distribution of the points for each country

ggplot(country_points, aes(country, points)) + 
  geom_boxplot() + 
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, colour = "steelblue", face = "bold"), axis.text.x = element_text(size = 8, colour = "black", angle = 40, vjust = 1, hjust = 1)) + 
  labs(title = "Wine Points vs Country of production", x = "Country of production", y = "Points")
```



```{r}
# we group by country, select the rows having max points for each country and further filter based on the criteria for quality wine 

quality_data <- 
  country_points %>% group_by(country) %>% 
  slice(which.max(points)) %>% 
  filter(points >= 90) 

quality_data
```
```{r}
# we can plot the graph of the maximum points from each countries

ggplot(quality_data, aes(country, points, size = price)) + 
  geom_point() + 
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, colour = "red", face = "bold"), axis.text.x = element_text(size = 10, colour = "black", angle = 40, vjust = 1, hjust = 1)) + 
  labs(title = "Highest points vs Country of production", x = "Country of production", y = "Points")
```


```{r}
# data sorted in descending order to easily see the countries with the highest points among the producers that meet the criteria

ordered_max <- quality_data[order(-quality_data$points), ] 
```

Australia, France, Italy Portugal and US make the best quality wine.


```{r}
# we install pacman package

install.packages("pacman")
```


```{r}
# we can present our data in a table

library(flextable) # we use flextable package from pacman
```
```{r}
flextable::flextable(ordered_max)

```

```{r}
# we can present the data for countries producing the best quality wines also as table

best_quality <- filter(ordered_max, points == 100)
flextable::flextable(best_quality)
```



```{r}
# any correlation between quality and price?

cor(country_points$points, country_points$price) # The quality of wine shows some moderate correlation with the price but not a perfect relationship.
```


### 2. To determine which products is the most expensive and which producer makes this

```{r}
# we select the desired columns and slice to obtain the most expensive wine

wine_prod <- filtered_data[c('country', 'designation', 'price', 'points')] %>% slice(which.max(price))

wine_prod[order(-wine_prod$price), ]
```
The most expensive product is Roger Rose Vineyard which is made in the US.


### 3. To determine products which should not be supplied anymore based on a benchmark of >=45 points


```{r}
products_filtered <- 
  filtered_data [c('designation', 'points')] %>% 
  filter(points <= 45)
                
view(products_filtered)

```
There are no products with points less than 45 therefore all products can continue to be supplied.


